Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-08-06 manuscript/manuscript.Rmd
Switching to Frontiers formatting

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author:
  - William Kumler,$^a$ Wei Qin,$^{a*}$ Rachel A. Lundeen,$^a$ Benedetto Barone,$^b$ Laura T. Carlson,$^a$ Anitra E. Ingalls$^a$#
output: 
  word_document:
    reference_docx: template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
csl: limnology-and-oceanography.csl
---

>>>>

---
title: "Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre"
author:
  - William Kumler,$^a$ Wei Qin,$^{a*}$ Rachel A. Lundeen,$^a$ Benedetto Barone,$^b$ Laura T. Carlson,$^a$ Anitra E. Ingalls$^a$#
output: 
  word_document:
    reference_docx: Frontiers_Template.docx
bibliography:
- Exported Items.bib
- r-packages.bib
csl: frontiers-in-marine-science.csl
---
